Heuristics and Really Hard Instances for Subgraph Isomorphism Problems

### 2016-04-12 paper/paper.tex
We're buying an extra page

%%% The lack of unsatisfiable instances cannot be addressed by using a pattern graph from one of the
%%% random suites with the ``wrong'' target graph: this tends to give either a trivially unsatisfiable
%%% instance, or a satisfiable instance. (In particular, it is \emph{not} the case that a relatively
%%% small random graph is unlikely to appear in a larger random graph.)

@@

The light line plots mean search effort using the Glasgow solver: for sparse patterns, the problem
is trivial, for dense patterns proving unsatisfiability is not particularly difficult, and we see a
complexity peak around the point where half the instances are satisfiable.  We also plot the search
cost of individual instances, as points. The behaviour we observe looks remarkably similar to random
3SAT problems---compare, for example, Figure 1 of \citet{LeytonBrown:2014}. In particular,
satisfiable instances tend to be easier, but show greater variation than unsatisfiable instances, and
there are exceptionally hard satisfiable instances \citep{Smith:1997}.

>>>>

The lack of unsatisfiable instances cannot be addressed by using a pattern graph from one of the
random suites with the ``wrong'' target graph: this tends to give either a trivially unsatisfiable
instance, or a satisfiable instance. (In particular, it is \emph{not} the case that a relatively
small random graph is unlikely to appear in a larger random graph.)

@@

The light line plots mean search effort using the Glasgow solver: for sparse patterns, the problem
is trivial, for dense patterns proving unsatisfiability is not particularly difficult, and we see a
complexity peak around the point where half the instances are satisfiable.  We also plot the search
cost of individual instances, as points. The behaviour we observe looks remarkably similar to random
3SAT problems---compare, for example, Figure 1 of \citet{LeytonBrown:2014}. In particular,
satisfiable instances tend to be easier, but show greater variation than unsatisfiable instances, and
there are exceptionally hard satisfiable instances \citep{Smith:1997}. (The Glasgow solver supports
parallel search with a work-stealing strategy explicitly designed to eliminate these. We have not
enabled this option to avoid dealing with the complexity of search tree measurements under
parallelism.)
